Global code motion of congruent instructions

### 2017-04-18 paper.tex
caption

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & size decrease in Bytes & size decrease in Bytes\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544  \\\hline
401.bzip2	& 1.00  & -1600  & 128  \\\hline
403.gcc	        & 1.00  & -58176 & 3384 \\\hline
429.mcf	        & 1.03  & 160    & 16   \\\hline
433.milc	& 1.00  & -656   & 224  \\\hline
444.namd	& 1.00  & -3864  & -1168\\\hline
445.gobmk	& 0.99  & -20480 & -264 \\\hline
447.dealII	& 0.95  & -27836 & 50934\\\hline
450.soplex	& 0.99  & 2220   & 348  \\\hline
453.povray	& 0.97  & 164    & -472 \\\hline
456.hmmer	& 0.99  & -3464  & -352 \\\hline
458.sjeng	& 1.02  & 440    & 1456 \\\hline
462.libquantum	& 1.00  & -96    & 0    \\\hline
464.h264ref	& 1.00  & -3424  & 864  \\\hline
470.lbm	        & 1.00  & 0      & 0    \\\hline
471.omnetpp	& 1.00  & 2688   & 200  \\\hline
473.astar	& 1.00  & -928   & 152  \\\hline
482.sphinx3	& 0.99  & 3008   & -176 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time (ratio) and code size change (bytes) with and without
    \gcm{} (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng;
    code size improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
  Benchmarks      &   Baseline	        & \GCM{}           & \%Decrease (low better) \\\hline
  400.perlbench	  &   186,829,426	& 184,690,006	& 0.99 \\\hline
  401.bzip2	  &   76,337,033	& 75,942,641	& 0.99 \\\hline
  403.gcc         &   1,079,625,231	& 1,073,158,220	& 0.99 \\\hline
  429.mcf         &   78,336,298	& 77,859,513	& 0.99 \\\hline
  433.milc	  &   272,525,306	& 269,684,876	& 0.99 \\\hline
  444.namd	  &   78,354,313	& 77,875,603	& 0.99 \\\hline
  445.gobmk	  &   261,229,078	& 258,459,798	& 0.99 \\\hline
  447.dealII	  &   643,457,797	& 638,628,331	& 0.99 \\\hline
  450.soplex	  &   245,442,755	& 242,811,500	& 0.99 \\\hline
  453.povray	  &   499,034,715	& 494,785,035	& 0.99 \\\hline
  456.hmmer	  &   214,425,324	& 211,984,389	& 0.99 \\\hline
  458.sjeng	  &   89,612,524	& 88,803,166	& 0.99 \\\hline
  462.libquantum  &   84,762,158	& 84,077,905	& 0.99 \\\hline
  464.h264ref	  &   151,049,588	& 149,284,624	& 0.99 \\\hline
  470.lbm         &   71,878,726	& 71,775,405	& 1.00 \\\hline
  471.omnetpp	  &   382,661,268	& 379,123,833	& 0.99 \\\hline
  473.astar	  &   78,351,117	& 77,872,820	& 0.99 \\\hline
  482.sphinx3	  &   158,434,290	& 156,586,406	& 0.99 \\\hline
  483.xalancbmk	  &   22,485,708,759	& 22,455,060,569& 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Change in total number of instructions executed during the
    compilation with and without \gcm{} (\GCM{}) on \SPEC{} at -Ofast.}
  \label{tab:compile-time}
\end{table}

>>>>

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & size decrease in Bytes & size decrease in Bytes\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544  \\\hline
401.bzip2	& 1.00  & -1600  & 128  \\\hline
403.gcc	        & 1.00  & -58176 & 3384 \\\hline
429.mcf	        & 1.03  & 160    & 16   \\\hline
433.milc	& 1.00  & -656   & 224  \\\hline
444.namd	& 1.00  & -3864  & -1168\\\hline
445.gobmk	& 0.99  & -20480 & -264 \\\hline
447.dealII	& 0.95  & -27836 & 50934\\\hline
450.soplex	& 0.99  & 2220   & 348  \\\hline
453.povray	& 0.97  & 164    & -472 \\\hline
456.hmmer	& 0.99  & -3464  & -352 \\\hline
458.sjeng	& 1.02  & 440    & 1456 \\\hline
462.libquantum	& 1.00  & -96    & 0    \\\hline
464.h264ref	& 1.00  & -3424  & 864  \\\hline
470.lbm	        & 1.00  & 0      & 0    \\\hline
471.omnetpp	& 1.00  & 2688   & 200  \\\hline
473.astar	& 1.00  & -928   & 152  \\\hline
482.sphinx3	& 0.99  & 3008   & -176 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}
  \end{center}
  \caption{Execution time (ratio) and code size change (Bytes) with and without
    \gcm{} (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng;
    code size improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \begin{tabular}{|l|c|c|c|}
      \hline
  Benchmarks      &   Baseline	        & \GCM{}           & \%Decrease (low better) \\\hline
  400.perlbench	  &   186,829,426	& 184,690,006	& 0.99 \\\hline
  401.bzip2	  &   76,337,033	& 75,942,641	& 0.99 \\\hline
  403.gcc         &   1,079,625,231	& 1,073,158,220	& 0.99 \\\hline
  429.mcf         &   78,336,298	& 77,859,513	& 0.99 \\\hline
  433.milc	  &   272,525,306	& 269,684,876	& 0.99 \\\hline
  444.namd	  &   78,354,313	& 77,875,603	& 0.99 \\\hline
  445.gobmk	  &   261,229,078	& 258,459,798	& 0.99 \\\hline
  447.dealII	  &   643,457,797	& 638,628,331	& 0.99 \\\hline
  450.soplex	  &   245,442,755	& 242,811,500	& 0.99 \\\hline
  453.povray	  &   499,034,715	& 494,785,035	& 0.99 \\\hline
  456.hmmer	  &   214,425,324	& 211,984,389	& 0.99 \\\hline
  458.sjeng	  &   89,612,524	& 88,803,166	& 0.99 \\\hline
  462.libquantum  &   84,762,158	& 84,077,905	& 0.99 \\\hline
  464.h264ref	  &   151,049,588	& 149,284,624	& 0.99 \\\hline
  470.lbm         &   71,878,726	& 71,775,405	& 1.00 \\\hline
  471.omnetpp	  &   382,661,268	& 379,123,833	& 0.99 \\\hline
  473.astar	  &   78,351,117	& 77,872,820	& 0.99 \\\hline
  482.sphinx3	  &   158,434,290	& 156,586,406	& 0.99 \\\hline
  483.xalancbmk	  &   22,485,708,759	& 22,455,060,569& 1.00 \\\hline
    \end{tabular}
  \end{center}
  \caption{Change in total number of instructions executed during the
    compilation with and without \gcm{} (\GCM{}) on \SPEC{} at -Ofast. The
    instructions were counted using valgrind.}
  \label{tab:compile-time}
\end{table}
